Compare CMC and HBCC differential expression

### 2017-08-26 code/Rmd/CMC_HBCC_COMPARISON.Rmd
Minor modifications

knit2synapse::knitToFolderEntity(file = "./CMC_HBCC_COMPARISON.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'CMC - HBCC - Reproducibility Analysis')
```

@@

### Analyse results
```{r anlz.results}
rep.rate = list()
for (pval in seq(0,-6,-1)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    dplyr::mutate(Direction = factor(sign(logFC), levels = c('-1','1'), labels = c('-1' = 'DOWN','1' = 'UP'))) %>%
    plyr::dlply(.(Model, Direction), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

@@

  rep.rate = c(rep.rate, list(data.frame(fdr = 10^pval, wo.qsva = wo.qsva, w.qsva = w.qsva,
                                         n.wo.qsva = n.wo.qsva, n.w.qsva = n.w.qsva)))
}
rep.rate = rbindlist(rep.rate)
rep.rate %>%
  dplyr::select(fdr, wo.qsva, w.qsva) %>%
  tidyr::gather(method, rep.rate, -fdr) %>%
  dplyr::mutate(rep.rate = rep.rate * 100) %>%
  dplyr::left_join(rep.rate %>%
                     dplyr::select(fdr, n.wo.qsva, n.w.qsva) %>%
                     tidyr::gather(method, ncount, -fdr) %>%
                     dplyr::mutate(method = gsub('n.','',method))) %>%
  dplyr::filter(fdr <= 1e-1) %>%
  ggplot(aes(x=fdr, y=rep.rate, size = ncount, color = method)) + geom_point() + geom_line() + scale_x_log10() + xlab('FDR') + ylab('Replication Rate (%)')
```

```{r anlz.results1}
rep.rate = list()
for (pval in c(-1, -1.30103, -2)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    plyr::dlply(.(Model), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

>>>>

knit2synapse::storeAndKnitToFileEntity(file = "./CMC_HBCC_COMPARISON.Rmd",
                                       parentId = "syn7501880",
                                       entityName = 'CMC - HBCC - Reproducibility Analysis')
```

@@

### Analyse results
Replication rate based on number of gene differentiallty expressed in the same directiona at an FDR of 0.05
```{r anlz.results}
rep.rate = list()
for (pval in seq(0,-6,-1)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    dplyr::mutate(Direction = factor(sign(logFC), levels = c('-1','1'), labels = c('-1' = 'DOWN','1' = 'UP'))) %>%
    plyr::dlply(.(Model, Direction), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

@@

  rep.rate = c(rep.rate, list(data.frame(fdr = 10^pval, wo.qsva = wo.qsva, w.qsva = w.qsva,
                                         n.wo.qsva = n.wo.qsva, n.w.qsva = n.w.qsva)))
}
rep.rate = rbindlist(rep.rate)
rep.rate %>%
  dplyr::select(fdr, wo.qsva, w.qsva) %>%
  tidyr::gather(method, rep.rate, -fdr) %>%
  dplyr::mutate(rep.rate = rep.rate * 100) %>%
  dplyr::left_join(rep.rate %>%
                     dplyr::select(fdr, n.wo.qsva, n.w.qsva) %>%
                     tidyr::gather(method, ncount, -fdr) %>%
                     dplyr::mutate(method = gsub('n.','',method))) %>%
  dplyr::filter(fdr <= 1e-1) %>%
  ggplot(aes(x=fdr, y=rep.rate, color = method)) + geom_point(aes(size = ncount)) + geom_line() + scale_x_log10() + xlab('FDR') + ylab('Replication Rate (%)')
```
Replication rate based on qvalue
```{r anlz.results1}
rep.rate = list()
for (pval in c(-1, -1.30103, -2)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    plyr::dlply(.(Model), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })
